Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-09 numerical-amr.tex
Edits to the overview section. Trying to unify notations, so several other sections are also affected.
Minor updates to the AMR section.  Moving ghost zone figure to this section.

@@

From the point of view of the hydro solver, each grid is solved as an independent CFD problem, with Dirichlet boundary conditions stored in the ghost zones.  At the end of each time step, cells on a given level fill ghost zones by interpolating from the parent and copying from neighbors on the same level.  Grids then correct the flux at the interface boundary between fine and coarse zones, and finally project their active zone data to the parent grid.

@@

\item{\em Baryon mass.}  This refinement criterion is designed to
  mimic a Lagrangian method in that it tries to keep a fixed mass
  resolution.  In this method, a cell is refined if the baryonic mass
  in the cell ($M_g = \rho\, (\Delta x)^d$) is larger than a specified value:
\begin{equation}
M_g > \rho_{\rm flag}\, (\Delta x_{\rm root})^d r^{\epsilon_l l},
\end{equation}
where $\rho_{\rm flag}$ is the equivalent density on the root grid required for refinement, $\Delta x_{\rm root}$ is the root grid cell spacing, $r$ is the refinement factor, $l$ is the level and $\epsilon_l$ is a parameter that can be used to make the refinement more aggressive ($\epsilon_l < 0$) or less aggressive than pure Lagrangian refinement ($\epsilon_l > 0$) -- in other words, super-Lagrangian or sub-Lagrangian in refinement.

@@

\item{\em Resistive length.}  In a way similar to the Jeans length criterion described above, the code can be forced to locally resolve the resistive length scale by a minimum of a fixed number of cells.  This is done by ensuring that the resistive length scale, defined as
\begin{equation}
L_R = |B| / |\nabla \times B|
\end{equation}
is always refined by at least N cells locally (i.e.~we refine a given cell further if $L_R \leq N \Delta x$).

@@

%From the point of view of the hydro solver, each grid is solved as an
%independent CFD problem, with Dirichlet boundary conditions stored in
%the ghost zones.  At the end of each time step, cells on a given level
%fill ghost zones by interpolating from the parent and copying from
%neighbors on the same level.  Grids then correct the flux at the interface boundary between
%fine and coarse zones, and finally project their real zone data to the
%parent grid.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/amr_hierarchy.eps}
\end{center}
\caption{\emph{Left:} Example of a simple, distributed AMR hierarchy
showing real and ghost grids.  \emph{Right:} Example 2D \enzo\ grid
showing real and ghost zones, as needed for the PPM hydro stencil. }
\label{fig.amr_hierarchy}
\end{figure}

@@

From the point of view of the hydro solver, each grid is solved as an independent CFD problem, with Dirichlet boundary conditions stored in the ghost zones.  At the end of each timestep, cells on a given level fill ghost zones by interpolating from the parent and copying from neighbors on the same level.  Grids then correct the flux at the interface boundary between fine and coarse zones, and finally project their active zone data to the parent grid.

@@

\item{\em Baryon mass.}  This refinement criterion is designed to
  mimic a Lagrangian method in that it tries to keep a fixed mass
  resolution.  In this method, a cell is refined if the baryonic mass
  in the cell ($M_g = \rho\, (\Delta x)^d$) is larger than a specified value:
\begin{equation}
M_g > \rho_{\rm flag}\, (\Delta x_{\rm root})^d r^{\epsilon_l l},
\end{equation}
where $\rho_{\rm flag}$ is the equivalent density on the root grid
required for refinement, $\Delta x_{\rm root}$ is the root grid cell
spacing, $r$ is the refinement factor, $l$ is the level and
$\epsilon_l$ is a parameter that can be used to make the refinement
more aggressive ($\epsilon_l < 0$) or less aggressive ($\epsilon_l >
0$) than pure Lagrangian refinement --- in other words,
super-Lagrangian or sub-Lagrangian in refinement.

@@

\item{\em Resistive length.}  In a way similar to the Jeans length criterion described above, the code can be forced to locally resolve the resistive length scale by a minimum of a fixed number of cells.  This is done by ensuring that the resistive length scale, defined as
\begin{equation}
L_R = |B| / |\curl B|
\end{equation}
is always refined by at least N cells locally (i.e.~we refine a given cell further if $L_R \leq N \Delta x$).

@@

%From the point of view of the hydro solver, each grid is solved as an
%independent CFD problem, with Dirichlet boundary conditions stored in
%the ghost zones.  At the end of each timestep, cells on a given level
%fill ghost zones by interpolating from the parent and copying from
%neighbors on the same level.  Grids then correct the flux at the interface boundary between
%fine and coarse zones, and finally project their real zone data to the
%parent grid.
